Brief notes on erosion

### 2020-07-29 docs/proposals/NSF/PostDocs/PI_change_request.tex
NM

I would like to request a restructuring of the NSF grant with Award
Number 2012560. PI Moore has left Florida State University (FSU) and
taken a faculty position at the US Naval Academy. Dr.~Moore's new
department does not have a graduate program, so the funded graduate
student's senior advisor will be co-PI Quaife at FSU. So that the grant
can be managed by FSU, I request that Dr.~Quaife becomes the lead PI and
Dr.~Moore becomes the co-PI. I also request permission for FSU to create
a sub-contract for the US Naval Academy that will manage Dr.~Moore's
funding.

>>>>

I would like to request a restructuring of the NSF grant with Award
Number 2012560. PI Moore has left Florida State University (FSU) and
taken a faculty position at the US Naval Academy. Dr.~Moore's new
department does not have a graduate program, so the funded graduate
student's senior advisor will be co-PI Quaife at FSU. So that the grant
can be managed by FSU, I request that Dr.~Quaife becomes the lead PI and
Dr.~Moore becomes the co-PI, with a sub-contract created for the US Naval Academy that will manage Dr.~Moore's funding.

% I also request permission for FSU to create a sub-contract for the US Naval Academy that will manage Dr.~Moore's funding.
